---
title: "COVID-19 across the World Shiny APP"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{COVID-19 Shiny APP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align='center'
)
```

This vignette describes the `shinyCovidWorld` package operation and how to launch the app, showing what the app does, and guidelines for its
use. 

The goal of `shinyCovidWorld` package is embedding a Shiny application dashboard about COVID-19 world data exploration and visualisation analysis. It makes it launching the application via a function exported by the own package. 

## Loading the `shinyCovidWorld` package

The first step before launching the app is to install the package from [GitHub](https://github.com/) with the following command:

``` {r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-prigrecov")
```

After that, the shiny application can be launched using the `launch_app()` function, which is the main component of the package:

```{r launch, eval=FALSE}
library(shinyCovidWorld)
launch_app()
```

This package also provides the code (inside the `inst/app/myapp` directory) and the dataset used by the interactive Shiny web application.  

The dataset used by the application is another component of this package. It is automatically loaded when the shiny application is launched. But the user can also acess it isolated as follows:

```{r dataset, eval=FALSE}
library(shinyCovidWorld)
covidData
```

Explore the contents in this website tabs to more detailed instructions on how to use the package and the functions contained within it.

## The Shiny Application - **COVID-19 Across The World** dashboard

The **COVID-19 Across The World** provides an overview analysis of the evolution of Coronavirus pandemic across the world using some interactive graphs and tables as visualisation tools for this. It was built using the Shiny framework in R. The purpose was to create an interactive and concise exploration in the Web-App format that can be easy to manipulate.

The raw input data used for this application are retrieved from this [GitHub repo](https://github.com/owid/covid-19-data/tree/master/public/data). The ["Our World in Data"](https://ourworldindata.org) is the organization that maintains this data, which is updated daily and includes data on confirmed cases, deaths, and testing, as well as other social and economic variables of potential interest from 210 countries and 6 continents across the world. The analysis period is from the end of December of 2019 up to 30 September 2020.

IInside the app, the user can explore and visualise the total or the daily number of cases and deaths recorded globally, continent by continent or country by country, through interactive graphs and tables which allow a customised data exploration according to the user interest.

The APP has two-panel tabs in its navigation bar. The 1st Tab shows the evolution of Covid-19 positive cases and deaths globally. The 2nd Tab progresses detailing the data by continent and by country, comparing the development of COVID-19 cases and deaths, in a daily and accumulated basis, through the six continents and 210 countries. The interactive graphs and tables allow updating the data and views according to the user’s selection (by shiny interaction options tools), permitting a customised data exploration as the reader interest.

The information is displayed using the following data visualisations:

* **PANEL 1: GLOBAL DATA**
In the first panel, we have two graphs displaying different data views ("Positive Cases" or "Deaths") to be chosen interactively by the user:

  * **Evolution of Positive Cases (or Deaths) in the World**: a double-y-axis plot displaying the evolution of daily data series and accumulated data series for the “Positive Cases” or “Deaths”.
  
  * **Global New Cases (or New Deaths) Distribution over the months**: a plot with a grid of density curves that summarises, for the data view selected by buttons ("Positive Cases" or "Deaths"), how the distribution of this data chosen series evolutes across the months. The vision permits analysing the monthly evolution of averages and dispersion/variance of the selected data.

* **PANEL 2: DATA BY CONTINENT AND COUNTRY**
In this second panel we have many options of interaction that allows the user selecting which statistic measure she wants to examine over 6 options: cases or deaths, daily or accumulated data, raw or smoothed data. Then, this selected statistic is plotted along with two graphs: 

  * **a multiple line chart by continent**, which permits analysing the evolution of the chosen statistic data over time and across all continents at the same time.

  * **a bar chart for the country** selected by the user (the 2nd option of interaction in this panel). Hence, this chart changes according to the user choices for country and statistic measure. The plot allows us to observe the combined evolution of the chosen data/statistic over time for each country selected by the user.
  
  * **a detailed interactive table** compiling the *complete daily time-series information of confirmed cases, deaths and tests, recorded in the daily and accumulated basis* for the selected country. 
  
  * **a summary static table** (for the same selected country) *aggregating the information* of the monthly average of new positive cases and deaths and the maximum levels achieved on the month — a summary view of average and maximum recordings evolution over the months, for each country.

<br>
More detailed instructions on how to use the applications and its content are provided within the app itself.

## Additionals
Any additional help or contribution to the package could be left as an [issue on Github](https://github.com/etc5523-2020/r-package-assessment-ltmoo2/issues) or sending me an email at pgre0007@student.monash.edu






